Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-22 conclusions.tex
Modifying conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1142 ccdd05d5-56c1-461a-bf98-85f6876523b4

Although we have demonstrated a feasible method for advance detection
\emph{filtering}, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.
% I don't understand what is trying to be said here.  Time-slices have no
% cross-correlation with eachother since they are orthogonal.
\begin{comment}If adjacent time slices have non-negligible cross-correlation
with each other, then there may be some subtleties in the design of these
postprocessing stages that we must address in order to translate the
early-warning outputs into candidate events.\end{comment}
%
As one possible method of addressing the latter, the time-slice decomposition
and the \SVD\ will help us form low-latency signal-based vetoes (for example, a
$\chi^2$ statistic) that have been essential for glitch rejection used in
previous \GW{} \CBC{} searches.

>>>>

Although we have demonstrated a feasible method for advance detection
\emph{filtering}, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.
% Drew: I don't understand what is trying to be said here.  Time-slices have no
% cross-correlation with eachother since they are orthogonal.
\begin{comment}If adjacent time slices have non-negligible cross-correlation
with each other, then there may be some subtleties in the design of these
postprocessing stages that we must address in order to translate the
early-warning outputs into candidate events.\end{comment}
%
However, we believe these obstacles are surmountable.
% Drew: Do we really want to say this. It doesn't really address any of the
% issues above.
\begin{comment}For an example of how the last obstacle could be approached, the
time-slice decomposition and the \SVD\ will help us form low-latency
signal-based vetoes (for example, a $\chi^2$ statistic) that have been
essential for glitch rejection used in previous \GW{} \CBC{}
searches.\end{comment}
